---
title: "About Me"
---

Hello! My name is LeonardK, and I am an MBA student at Baruch College.

My academic and professional interests lie at the intersection of business strategy, analytics, and technology. I am particularly interested in how data-driven decision-making can help organizations identify opportunities, improve operational performance, and address complex business problems.

This website serves as a portfolio for my work in STA 9750, where I will document projects and analyses completed throughout the semester using tools such as R, Quarto, Git, and GitHub.

Outside of coursework, I enjoy expanding my knowledge of emerging technologies, financial markets, and the evolving role of analytics in business.



```{r}
#| echo: false
#| message: false
#| warning: false

if(!require("leaflet")){
    options(repos=c(CRAN="https://cloud.r-project.org"))
    install.packages("leaflet")
    stopifnot(require("leaflet"))
}

baruch_longitude <- -73.98333
baruch_latitude  <- +40.74028

leaflet() |>
  addTiles() |>
  setView(baruch_longitude, baruch_latitude, zoom=17) |>
  addPopups(baruch_longitude, baruch_latitude, 
            "I am a Master's student at <b>Baruch College</b>!")
```





```{r}
#| include: false
1+1
```
--------------
Last Updated: `r format(Sys.time(), "%A %m %d, %Y at %H:%M%p")`

